---
title: "PIP data update on May 9, 2022"
description: |
  This intermediate PIP update corrects several errors as documented in this post.
categories:
  - Data update
author:
  - name: PIP Technical Team
date: 2022-05-09
output:
  distill::distill_article:
    toc: true
    number_sections: true
    toc_depth: 4
    # code_folding: true
    toc_float: true
    collapsed: false
    smooth_scroll: true
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(data.table)
library(knitr)
library(kableExtra)
```

## Survey-year estimates for Fiji 2019

The consumption aggregate has been revised to include all relevant non-food
expenditures. In the previous version, non-food expenditures in four categories
(utilities, communication services, domestic services, and education) were not
fully accounted for with all households, leading to an underestimation of total
consumption. The upward revision in the consumption aggregate reduces the
poverty rates and leads to a small upward revision of the Gini index.

```{r table}
dt <- tibble::tribble(
  ~country, ~year,                  ~measure,   ~date, ~value,
    "Fiji", 2019L, "Poverty headcount $1.90", "8-Apr",    2.6,
    "Fiji", 2019L, "Poverty headcount $1.90", "2-May",   1.85,
    "Fiji", 2019L, "Poverty headcount $3.20", "8-Apr",  17.79,
    "Fiji", 2019L, "Poverty headcount $3.20", "2-May",   14.5,
    "Fiji", 2019L, "Poverty headcount $5.50", "8-Apr",  55.54,
    "Fiji", 2019L, "Poverty headcount $5.50", "2-May",  49.43,
    "Fiji", 2019L,              "Gini Index", "8-Apr",  30.14,
    "Fiji", 2019L,              "Gini Index", "2-May",  30.71
  )
setDT(dt)
df <- dt[, c("measure", "date", "value")]
df <- dcast(df, measure ~ date)
```

```{r}
kable(df, col.names = c("", "09 May", "08 April")) 
```

## Changes to national accounts data

Four changes have been made to the national accounts data, which affects the
reference-year series for several countries. First, due to an error in the data,
the GDP per capita value for Somalia in 2011 has been removed.

Second, previously when WEO had information on total GDP but no population
estimates, and hence no information on GDP per capita, GDP per capita was
inferred using population estimates from WDI. This is no longer done because the
population series from WDI may be different from the population series WEO uses
in adjacent years to compute GDP per capita, which could create unrealistic
trends in growth in GDP per capita. As a consequence of this change, there is
now no national accounts estimate for Samoa in 1981 and estimates for Guinea
before 1990 rely on the Maddison Project Database rather than WEO.

Third, the vintage of the WDI national accounts data used for India has been
updated to 15 February 2022, which is consistent with the vintage used for all
other countries. This affects the reference-year series for India slightly.

Fourth, the February version of WDI also includes national accounts data for the
Syrian Arab Republic, which are now being used in the reference-year series.
Previously, WDI did not include national accounts data for the Syrian Arab
Republic, so alternative estimates were used (for further details on the earlier
estimates, see [this
document](https://documents1.worldbank.org/curated/en/099422404082231105/pdf/IDU02070690808ee7044720a1e6010de398e6a75.pdf)).

## Changes to metadata

-   The comparability indicator for Nigeria has been corrected. It now shows a
    break in comparability between the 2015/16 and 2018/19 surveys.

-   The comparability indicator for Maldives has been corrected. It now shows a
    break in comparability between the 2016 and 2019 surveys

## Changes to country profiles

For Russia, the country profiles page now shows the consumption trend
(previously, the income trend was shown). In the poverty calculator, both trends
are available.
