---
title: "PIP Data Revisions to data from 15 February 2022"
description: |
  This document tracks the revisions that have been made to the data in the World Bank’s Poverty and Inequality Platform. In a typical year, there are two major updates (in March/April and September/October), which bring in new survey data. These major updates are documented using a What’s New document (published in the Global Poverty Monitoring Technical Notes series). When necessary, intermediate updates are made to correct errors as soon as possible. Changes made as part of the intermediate updates are documented below. 
categories:
  - Data revision
author:
  - name: PIP Technical Team
date: 2022-05-02
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(data.table)
library(knitr)
library(kableExtra)
```

# 2 May, 2022

Update to correct the following errors:

## Survey-year estimates for Fiji 2019

The consumption aggregate has been revised to include all relevant non-food
expenditures. In the previous version, non-food expenditures in four categories
(utilities, communication services, domestic services, and education) were not
fully accounted for with all households, leading to an underestimation of total
consumption. The upward revision in the consumption aggregate reduces the
poverty rates and leads to a small upward revision of the Gini index.

```{r table}
dt <- tibble::tribble(
  ~country, ~year,                  ~measure,   ~date, ~value,
    "Fiji", 2019L, "Poverty headcount $1.90", "8-Apr",    2.6,
    "Fiji", 2019L, "Poverty headcount $1.90", "2-May",   1.85,
    "Fiji", 2019L, "Poverty headcount $3.20", "8-Apr",  17.79,
    "Fiji", 2019L, "Poverty headcount $3.20", "2-May",   14.5,
    "Fiji", 2019L, "Poverty headcount $5.50", "8-Apr",  55.54,
    "Fiji", 2019L, "Poverty headcount $5.50", "2-May",  49.43,
    "Fiji", 2019L,              "Gini Index", "8-Apr",  30.14,
    "Fiji", 2019L,              "Gini Index", "2-May",  30.71
  )
setDT(dt)
df <- dt[, c("measure", "date", "value")]
df <- dcast(df, measure ~ date)
```

```{r}
kable(df, col.names = c("", "02 May", "08 April")) 
```

## Changes to national accounts data

Due to an error in the data, the GDP per capita for Somalia in 2011 has been
removed, which affects the reference-year series for Somalia. The vintage of the
WDI national accounts data used for India has been updated to 15 February 2022,
which is consistent with the vintage used for all other countries. This affects
the reference-year series for India slightly

## Changes to metadata

-   The comparability indicator for Nigeria has been corrected. It now shows a
    break in comparability between the 2015/16 and 2018/19 surveys.

-   The comparability indicator for Maldives has been corrected. It now shows a
    break in comparability between the 2016 and 2019 surveys

## Changes to country profiles

For Russia, the country profiles page now shows the consumption trend
(previously, the income trend was shown). In the poverty calculator, both trends
are available.

# 08 April, 2022

The semi-annual update to PIP presents new global poverty estimates for 2018 and
revises previously published estimates, as a result of newly available survey
data (a large number of new country-years have been added) and several changes
to the underlying data. Further details on the changes are available in [this
document](https://documents.worldbank.org/en/publication/documents-reports/documentdetail/099422404082231105/idu02070690808ee7044720a1e6010de398e6a75).
